Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-06 manuscript.tex
20161106

\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. \textcolor{red}{$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the roll and pitch dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$. $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively, and $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

This section have established the deployment dynamics with the input limitation and an adaptive saturated sliding mode control law will be presented in the subsequent section.

@@

\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with ignoring the input limitation, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:

@@

In the low orbit altitude, the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque. Thanks to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm. The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}. Hence, the external disturbance can be described by the following expression

@@

Therefore, the bounded external disturbance satisfy

@@

and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$. The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can chose the function $y = x+arcsin(\Delta h)$ to obtain following relations:

@@

where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties. $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$. $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.  In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity. In Fig~\ref{fig:6}, although the dynamics have been already stable, the tension is switching in the high frequency. It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where

>>>>

\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. \textcolor{red}{$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the roll and pitch dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$. $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively. $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

This section has established the deployment dynamics with the input limitation and an adaptive saturated sliding mode control law will be presented in the subsequent section.

@@

\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with the input limitation ignored, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:

@@

In low-altitude orbit , the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque. Thanks to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm. The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}. Hence, the external disturbance can be described by the following expression

@@

Therefore, the bounded external disturbance satisfies

@@

and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$. The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+arcsin(\Delta h)$ to obtain following relations:

@@

where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties. $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$. $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.  In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity. In Fig~\ref{fig:6}, although the dynamics have already been  stable, the tension is switching in the high frequency. It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
